Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-18 cloneoverflow-latex/cloneoverflow.tex
(Section 2) merged the Experimental Framework and Experimental Setup together.

\subsection{Experimental Framework}

To answer the four research questions, we used the experimental
framework depicted in \Cref{fig:exp_framework}. We processed two
datasets, 144,064 Java code snippets from accepted answers on Stack
Overflow and 111 open source projects from the Qualitas corpus. The
Java code snippets were extracted from Stack Overflow posts. We
prepared the Java code in both datasets by removing comments and
pretty-printing to increase the accuracy of clone detection. Then, we
deployed two clone detection tools, Simian~\cite{simian} and
NiCad~\cite{Roy2008,Cordy}, to locate clones between the two datasets.
Due to the scalability of Simian and NiCad, we partitioned the input
and run the tools multiple times. Each run was composed of the whole
Stack Overflow data and a single Qualitas project. We repeated the
process until we covered all 111 projects.

%enabled us to reuse the same scripts to analyse clone reports from both Simian and NiCad. Moreover, using GCF, other additional clone detectors could be adopted
We then converted the clone reports to the General Clone Format
(GCF)~\cite{Wang2013} and combined the 111 reports into a single GCF
file.
% GCF provides a common format for clone reports which enables other
% clone detectors to be adopted, if needed, without any changes in the
% analysis.
Simian did not provide an option to detect cross-project clones
between two locations. Hence the Simian GCF clone report was filtered
to contain only clone pairs between Stack Overflow and Qualitas
projects, removing all clone pairs within either Stack Overflow or
within Qualitas. NiCad provides an option to detect clones from two
locations so no filtering was needed. We did not have an oracle of clones
between the two data sets so we rely on a manual investigation to
validate the reported clone candidates. However, the large amount of
generated clone pairs hindered us from looking at all of them.
% A random sampling of clones could have been employed, however, the
% risk of returning false positives non-meaningful clones is
% increased.
Instead of extracting a random sample, we selected clone pair
candidates by relying on \emph{agreement} of clone detectors. If a
clone pair was reported by multiple tools, we had a higher
confidence that it was a real clone pair. To achieve this, clone pairs
from the two clone detectors were pair-wise matched to find agreements
using Bellon's clone overlapping criteria~\cite{Bellon2007}. This step
generated \textbf{agreed clone
  pairs}. They were pairs with high confidence to be true clones since
they obtained agreement from both tools. Then, pairs reported by
Simian and NiCad that did not find agreement were categorised as
\textbf{disagreed clone pairs}. The disagreed clone pairs were clones
with less confidence than the agreed ones. Finally, agreed and
disagreed clone pairs have been looked at manually by two of the
authors.

In the manual inspection process, we classified clones into seven
categories according to information observed from code comments and
text in the Stack Overflow answer. This process took approximately a
month until we successfully investigated 3,632 clone pairs. Clone
pairs that were classified as false clones, boiler-plate code, or
IDE-generated are not very interesting and were ignore in the analysis
of outdated code and licensing violation. We compared the licensing
information of the 668 remaining clone pairs for possibilities of software
licensing violations. Moreover, we looked at the history starting at
the date of the answers to today from its git repository. With this
method, we discovered \textbf{outdated code}, i.e.~code that changes
were made to them after they have been copied to Stack
Overflow. %hence resulting in outdated clones on Stack Overflow.

\subsection{Experimental Setup}

We followed the experimental framework by processing the source code from the two data sets, configuring and running the clone detectors, and analysing the clones. We discuss each of them in details below.

\subsubsection{Datasets}

\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of a Stack Overflow dump\footnote{https://archive.org/details/stackexchange} in January 2016. The archived dump has a size of 9 gigabytes. The data dump was in XML format containing information of \textbf{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts. We were interested in code snippets embedded in posts which were located between {\small\texttt{<code></code>}} tags. A Stack Overflow thread contains a post of a question and several posts of answers where every answer has voting score from its users. An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem. We collected Java code snippets using two criteria. First, we were only interested in code snippets with at least six lines. Snippets that are smaller than six lines are usually spurious clones~\cite{Bellon2007}. Second, we only focused on code snippets in accepted answers. We chose the snippets in accepted answers because they actually solved the problems in the questions. Moreover, they are always displayed just below the questions which makes them more attractive to be reused than other answers. Each snippet was extracted from the dump and saved to a file. 
%using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. 
We obtained 144,064 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.

@@

\subsubsection{Clone Detectors}
There is a number of restrictions in terms of choosing clone detection tools for this study. The main restriction is due to nature of code snippets posted on Stack Overflow, most of them are not complete Java classes or methods. Hence, the tool must be flexible enough to process code snippets that are neither a complete block nor compilable. Moreover, since the amount of code that has to be processed is in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time. We have tried 5 state-of-the-art clone detectors including Simian~\cite{simian}, NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against Stack Overflow and Qualitas datasets. CCFinder, iClones, and DECKARD failed with execution errors after running for couple of hours. Thus, we removed them from the study. Simian and NiCad completed the detection with success. We found that both of them are also flexible enough to handle code with incomplete methods or classes. %So, we decided to use both of them.

@@

\subsubsection{Prioritise Clone Candidates Using Agreement}
The number of clones detected in large-scale datasets can be huge. In our study, there are in total 266,837,480 clone pairs reported. It is infeasible for humans to manually validate them all. One can do a random sampling of clones. However, due to a very high number of false positives, they may end up looking mostly at the false clones. Therefore, we adopted the idea of \textbf{clone agreement} which has been used in clone research studies~\cite{Wang2013,Funaro2010,cr2016ssbse} in situations where a clone oracle is missing or impossible to establish. Clone pairs agreed by multiple clone detection tools have a higher confidence to be real clones~\cite{cr2016ssbse}. By using this agreement-based approach, we could reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools. To find an agreement between two clone pairs reported by two different tools, we used the clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have a large enough number of overlapping clone lines can be categorised as either a good-match or an ok-match pair (denoted as \textit{good} and \textit{ok} respectively) with a confident value between 0 and 1. A \textit{good} clone pair has stronger agreement than an \textit{ok} pair. We follow the original definitions of \textit{good}- and \textit{ok}-match introduced in Bellon's paper~\cite{Bellon2007}.

@@

Using this good and ok-match criteria with a predefined threshold \textit{p}, we can prune the 266 million candidate clone pairs for manual investigation. \textit{good} pairs are the ones with the highest confidence and are ranked first to be looked at, followed by \textit{ok} pairs, and followed by clone pairs without agreement.

@@

>>>>

%\subsection{Experimental Setup}
\vspace{1ex}
To answer these four research questions, we perform an experiment to
locate and study the online code clones between Stack Overflow and open source
projects. The experimental framework is depicted in \Cref{fig:exp_framework}. 
We discuss the experimental setup below.

%\subsection{Experimental Setup}

%We followed the experimental framework by processing the source code from the two data sets, configuring and running the clone detectors, and analysing the clones. We discuss each of them in details below.

\subsection{Datasets}

We reply on two data sets in this study: Java code snippets on Stack Overflow and open source projects from the Qualitas corpus.

\subsubsection{Stack Overflow} we extracted Java code snippets from a snapshot of a Stack Overflow dump\footnote{https://archive.org/details/stackexchange} in January 2016. The archived dump has a size of 9 gigabytes. The data dump was in XML format containing information of \textbf{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts. We were interested in code snippets embedded in posts which were located between {\small\texttt{<code></code>}} tags. A Stack Overflow thread contains a post of a question and several posts of answers where every answer has voting score from its users. An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem. We collected Java code snippets using two criteria. First, we were only interested in code snippets with at least six lines. Snippets that are smaller than six lines are usually spurious clones~\cite{Bellon2007}. Second, we only focused on code snippets in accepted answers. We chose the snippets in accepted answers because they actually solved the problems in the questions. Moreover, they are always displayed just below the questions which makes them more attractive to be reused than other answers. Each snippet was extracted from the dump and saved to a file. 
%using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. 
We obtained 144,064 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.

@@

\subsection{Clone Detectors}
There is a number of restrictions in terms of choosing clone detection tools for this study. The main restriction is due to nature of code snippets posted on Stack Overflow, most of them are not complete Java classes or methods. Hence, the tool must be flexible enough to process code snippets that are neither a complete block nor compilable. Moreover, since the amount of code that has to be processed is in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time. We have tried 5 state-of-the-art clone detectors including Simian~\cite{simian}, NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against Stack Overflow and Qualitas datasets. CCFinder, iClones, and DECKARD failed with execution errors after running for couple of hours. Thus, we removed them from the study. Simian and NiCad completed the detection with success. We found that both of them are also flexible enough to handle code with incomplete methods or classes. %So, we decided to use both of them.

@@

%We processed two datasets, 144,064 Java code snippets from accepted answers on Stack
%Overflow and 111 open source projects from the Qualitas corpus. 
%The Java code snippets were extracted from Stack Overflow posts. 
We prepared the Java code in both datasets by removing comments and
pretty-printing to increase the accuracy of clone detection. Then, we
deployed two clone detection tools to locate clones between the two datasets.
Due to the scalability of Simian and NiCad, we partitioned the input
and run the tools multiple times. Each run was composed of the whole
Stack Overflow data and a single Qualitas project. We repeated the
process until we covered all 111 projects.
We then converted the clone reports to the General Clone Format
(GCF)~\cite{Wang2013} and combined the 111 reports into a single GCF
file.
Simian did not provide an option to detect cross-project clones
between two locations. Hence the Simian GCF clone report was filtered
to contain only clone pairs between Stack Overflow and Qualitas
projects, removing all clone pairs within either Stack Overflow or
within Qualitas. NiCad provides an option to detect clones from two
locations so no filtering was needed.

\subsection{Prioritise Clone Candidates Using Agreement}
The number of clones detected in large-scale datasets can be huge. In our study, there are in total 315,786,118 clone pairs reported. It is infeasible for humans to manually validate them all. One can do a random sampling of clones. However, due to a very high number of false positives, they may end up looking mostly at the false clones. Therefore, we adopted the idea of \textbf{clone agreement} which has been used in clone research studies~\cite{Wang2013,Funaro2010,cr2016ssbse} in situations where a clone oracle is missing or impossible to establish. Clone pairs agreed by multiple clone detection tools have a higher confidence to be real clones~\cite{cr2016ssbse}. By using this agreement-based approach, we could reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools. To find an agreement between two clone pairs reported by two different tools, we used the clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have a large enough number of overlapping clone lines can be categorised as either a good-match or an ok-match pair (denoted as \textit{good} and \textit{ok} respectively) with a confident value between 0 and 1. A \textit{good} clone pair has stronger agreement than an \textit{ok} pair. We follow the original definitions of \textit{good}- and \textit{ok}-match introduced in Bellon's paper~\cite{Bellon2007}.

@@

Using this good and ok-match criteria with a predefined threshold \textit{p}, we can prune the 315 million candidate clone pairs for manual investigation. \textit{good} pairs are the ones with the highest confidence, followed by \textit{ok} pairs, and followed by clone pairs without agreement. We call the 
\textit{good} and \textit{ok} pairs \textbf{agreed} clone pairs and the the clone pairs reported by Simian and NiCad without agreement \textbf{disagreed} clone pairs.

@@

%\subsection{Manual Investigation}
%We did not have an oracle of clones
%between the two data sets so we rely on a manual investigation to
%validate the reported clone candidates. However, the large amount of
%generated clone pairs hindered us from looking at all of them.
%A random sampling of clones could have been employed, however, the 
%risk of returning false positives non-meaningful clones is increased.
%Instead of extracting a random sample, we selected clone pair
%candidates by relying on \emph{agreement} of clone detectors. If a
%clone pair was reported by multiple tools, we had a higher
%confidence that it was a real clone pair. To achieve this, clone pairs
%from the two clone detectors were pair-wise matched to find agreements
%using Bellon's clone overlapping criteria~\cite{Bellon2007}. This step
%generated 
%\textbf{agreed clone pairs}. They were pairs with high confidence to be true clones since
%they obtained agreement from both tools. Then, pairs reported by
%Simian and NiCad that did not find agreement were categorised as
%\textbf{disagreed clone pairs}. The disagreed clone pairs were clones
%with less confidence than the agreed ones. 
%Finally, agreed and
%disagreed clone pairs have been looked at manually by two of the
%authors.

%In the manual inspection process, we classified clones into seven
%categories according to information observed from code comments and
%text in the Stack Overflow answer. This process took approximately a
%month until we successfully investigated 3,632 clone pairs. Clone
%pairs that were classified as false clones, boiler-plate code, or
%IDE-generated are not very interesting and were ignore in the analysis
%of outdated code and licensing violation. We compared the licensing
%information of the 668 remaining clone pairs for possibilities of software
%licensing violations. Moreover, we looked at the history starting at
%the date of the answers to today from its git repository. With this
%method, we discovered \textbf{outdated code}, i.e.~code that changes
%were made to them after they have been copied to Stack
%Overflow. 
%hence resulting in outdated clones on Stack Overflow.
